---
title: "comp_management"
author: "Shimin Gu"
date: "2024-08-28"
output: html_document
---

```{r}
#load package
library(ggplot2)
library(dplyr)
library(rstatix)
library(gridExtra)
library(grid)
library(tidyverse)
library(caret)
library(ggrepel)
library(ggpmisc)
library(mgcv)

#load data
mag_ssp1_st <- read.csv("manage_country_ssp1_st.csv", sep = ",", header = T);mag_ssp1_st$group <- "ssp1_st"
mag_ssp1_dy <- read.csv("manage_country_ssp1_dy.csv", sep = ",", header = T);mag_ssp1_dy$group <- "ssp1_dy"
mag_ssp2_st <- read.csv("manage_country_ssp2_st.csv", sep = ",", header = T);mag_ssp2_st$group <- "ssp2_st"
mag_ssp2_dy <- read.csv("manage_country_ssp2_dy.csv", sep = ",", header = T);mag_ssp2_dy$group <- "ssp2_dy"
mag_ssp5_st <- read.csv("manage_country_ssp5_st.csv", sep = ",", header = T);mag_ssp5_st$group <- "ssp5_st"
mag_ssp5_dy <- read.csv("manage_country_ssp5_dy.csv", sep = ",", header = T);mag_ssp5_dy$group <- "ssp5_dy"

manage_sce <- read.csv("manage scenarios.csv", sep = ",", header = T)



bind_reg_mag_ssps_st <- read.csv("bind_reg_mag_ssps_st_new.csv", sep = ",", header = T)

```

#normality test
```{r}
#mag_ssp1_st
shapiro_test <- shapiro.test(mag_ssp1_st$pred_cost_mean)
mag_ssp1_st$log_pred_cost_mean <- log10(mag_ssp1_st$pred_cost_mean + 1)
shapiro_test <- shapiro.test(mag_ssp1_st$log_pred_cost_mean)
shapiro_test

#mag_ssp1_dy
shapiro_test <- shapiro.test(mag_ssp1_dy$pred_cost_mean)
mag_ssp1_dy$log_pred_cost_mean <- log10(mag_ssp1_dy$pred_cost_mean + 1)
shapiro_test <- shapiro.test(mag_ssp1_dy$log_pred_cost_mean)
shapiro_test

#mag_ssp2_st
shapiro_test <- shapiro.test(mag_ssp2_st$pred_cost_mean)
mag_ssp2_st$log_pred_cost_mean <- log10(mag_ssp2_st$pred_cost_mean + 1)
shapiro_test <- shapiro.test(mag_ssp2_st$log_pred_cost_mean)
shapiro_test

#mag_ssp2_dy
shapiro_test <- shapiro.test(mag_ssp2_dy$pred_cost_mean)
mag_ssp2_dy$log_pred_cost_mean <- log10(mag_ssp2_dy$pred_cost_mean + 1)
shapiro_test <- shapiro.test(mag_ssp2_dy$log_pred_cost_mean)
shapiro_test

#mag_ssp5_st
shapiro_test <- shapiro.test(mag_ssp5_st$pred_cost_mean)
mag_ssp5_st$log_pred_cost_mean <- log10(mag_ssp5_st$pred_cost_mean + 1)
shapiro_test <- shapiro.test(mag_ssp5_st$log_pred_cost_mean)
shapiro_test

#mag_ssp5_dy
shapiro_test <- shapiro.test(mag_ssp5_dy$pred_cost_mean)
mag_ssp5_dy$log_pred_cost_mean <- log10(mag_ssp5_dy$pred_cost_mean + 1)
shapiro_test <- shapiro.test(mag_ssp5_dy$log_pred_cost_mean)
shapiro_test
```


#And found without normality, using non-parameteric paired test
#_tot_
```{r}
#mag_ssp1_st
mag_ssp1_st <- mag_ssp1_st %>%
  arrange(match(mag_ssp1_st$Country_name, mag_ssp1_dy$Country_name))
bind_mag_ssp1_st <- rbind(mag_ssp1_st,mag_ssp1_dy)
bind_mag_ssp1_st %>%
  wilcox_test(pred_cost_mean ~ group, paired = TRUE)

#mag_ssp2_st
mag_ssp2_st <- mag_ssp2_st %>%
  arrange(match(mag_ssp2_st$Country_name, mag_ssp2_dy$Country_name))
bind_mag_ssp2_st <- rbind(mag_ssp2_st,mag_ssp2_dy)
bind_mag_ssp2_st %>%
  wilcox_test(pred_cost_mean ~ group, paired = TRUE)

#mag_ssp5_st
mag_ssp5_st <- mag_ssp5_st %>%
  arrange(match(mag_ssp5_st$Country_name, mag_ssp5_dy$Country_name))
bind_mag_ssp5_st <- rbind(mag_ssp5_st,mag_ssp5_dy)
bind_mag_ssp5_st %>%
  wilcox_test(pred_cost_mean ~ group, paired = TRUE)

```


# plotting data preparing
#violin + scatter
#_tot_
```{r}
#mag_ssp1_st
mag_ssp1_st <- mag_ssp1_st %>%
  arrange(match(mag_ssp1_st$Country_name, mag_ssp1_dy$Country_name))
mag_ssp1_st$direct <- 0
mag_ssp1_st$ssp1_pred <- mag_ssp1_st$pred_cost_mean
mag_ssp1_st$change <- mag_ssp1_st$ssp1_pred-mag_ssp1_dy$pred_cost_mean
mag_ssp1_st$propchange <-(mag_ssp1_st$ssp1_pred-mag_ssp1_dy$pred_cost_mean)/mag_ssp1_dy$pred_cost_mean
for (i in 1:67){
  if(mag_ssp1_st$change[i]>0){mag_ssp1_st$direct[i] = "increase"}
  if(mag_ssp1_st$change[i]<0){mag_ssp1_st$direct[i] = "decrease"}
  if(mag_ssp1_st$change[i]==0){mag_ssp1_st$direct[i] = "no change"}
}
reg_mag_ssp1_st <- mag_ssp1_st
mag_ssp1_st <- mag_ssp1_st[,1:4]
mag_ssp1_dy$direct <- mag_ssp1_st$direct
bind_mag_ssp1_st <- rbind(mag_ssp1_st,mag_ssp1_dy)

#mag_ssp2_st
mag_ssp2_st <- mag_ssp2_st %>%
  arrange(match(mag_ssp2_st$Country_name, mag_ssp2_dy$Country_name))
mag_ssp2_st$direct <- 0
mag_ssp2_st$ssp2_pred <- mag_ssp2_st$pred_cost_mean
mag_ssp2_st$change <- mag_ssp2_st$ssp2_pred-mag_ssp2_dy$pred_cost_mean
mag_ssp2_st$propchange <-(mag_ssp2_st$ssp2_pred-mag_ssp2_dy$pred_cost_mean)/mag_ssp2_dy$pred_cost_mean
for (i in 1:67){
  if(mag_ssp2_st$change[i]>0){mag_ssp2_st$direct[i] = "increase"}
  if(mag_ssp2_st$change[i]<0){mag_ssp2_st$direct[i] = "decrease"}
  if(mag_ssp2_st$change[i]==0){mag_ssp2_st$direct[i] = "no change"}
}
reg_mag_ssp2_st <- mag_ssp2_st
mag_ssp2_st <- mag_ssp2_st[,1:4]
mag_ssp2_dy$direct <- mag_ssp2_st$direct
bind_mag_ssp2_st <- rbind(mag_ssp2_st,mag_ssp2_dy)

#mag_ssp5_st
mag_ssp5_st <- mag_ssp5_st %>%
  arrange(match(mag_ssp5_st$Country_name, mag_ssp5_dy$Country_name))
mag_ssp5_st$direct <- 0
mag_ssp5_st$ssp5_pred <- mag_ssp5_st$pred_cost_mean
mag_ssp5_st$change <- mag_ssp5_st$ssp5_pred-mag_ssp5_dy$pred_cost_mean
mag_ssp5_st$propchange <-(mag_ssp5_st$ssp5_pred-mag_ssp5_dy$pred_cost_mean)/mag_ssp5_dy$pred_cost_mean
for (i in 1:67){
  if(mag_ssp5_st$change[i]>0){mag_ssp5_st$direct[i] = "increase"}
  if(mag_ssp5_st$change[i]<0){mag_ssp5_st$direct[i] = "decrease"}
  if(mag_ssp5_st$change[i]==0){mag_ssp5_st$direct[i] = "no change"}
}
reg_mag_ssp5_st <- mag_ssp5_st
mag_ssp5_st <- mag_ssp5_st[,1:4]
mag_ssp5_dy$direct <- mag_ssp5_st$direct
bind_mag_ssp5_st <- rbind(mag_ssp5_st,mag_ssp5_dy)

bind_mag_ssp1_st$group <- factor(bind_mag_ssp1_st$group, levels = c("ssp1_st","ssp1_dy"))
bind_mag_ssp2_st$group <- factor(bind_mag_ssp2_st$group, levels = c("ssp2_st","ssp2_dy"))
bind_mag_ssp5_st$group <- factor(bind_mag_ssp5_st$group, levels = c("ssp5_st","ssp5_dy"))
```

#non-linear regression
#_tot_
```{r}
# reg_mag_ssp1_st <- reg_mag_ssp1_st[,c(1,7)]
# reg_mag_ssp1_st$mag <- 0
# for (i in 1:67){
#   for (j in 1:67){
#     if (reg_mag_ssp1_st$Country_name[i] == manage_sce$Official_country_sumssp1[j])
#     {reg_mag_ssp1_st$mag[i] = manage_sce$ssp1_sum_manag[j];break}
#   }
# }
# 
# reg_mag_ssp2_st <- reg_mag_ssp2_st[,c(1,7)]
# reg_mag_ssp2_st$mag <- 0
# for (i in 1:67){
#   for (j in 1:67){
#     if (reg_mag_ssp2_st$Country_name[i] == manage_sce$Official_country_sumssp2[j])
#     {reg_mag_ssp2_st$mag[i] = manage_sce$ssp2_sum_manag[j];break}
#   }
# }
# 
# reg_mag_ssp5_st <- reg_mag_ssp5_st[,c(1,7)]
# reg_mag_ssp5_st$mag <- 0
# for (i in 1:67){
#   for (j in 1:67){
#     if (reg_mag_ssp5_st$Country_name[i] == manage_sce$Official_country_sumssp5[j])
#     {reg_mag_ssp5_st$mag[i] = manage_sce$ssp5_sum_manag[j];break}
#   }
# }
# reg_mag_ssp1_st$log_mag <- log10(reg_mag_ssp1_st$mag + 1)
# reg_mag_ssp2_st$log_mag <- log10(reg_mag_ssp2_st$mag + 1)
# reg_mag_ssp5_st$log_mag <- log10(reg_mag_ssp5_st$mag + 1)
# reg_mag_ssp1_st$group <- "ssp1"
# reg_mag_ssp2_st$group <- "ssp2"
# reg_mag_ssp5_st$group <- "ssp5"
# 
# bind_reg_mag_ssps_st <- rbind(reg_mag_ssp1_st,reg_mag_ssp2_st,reg_mag_ssp5_st)
```

#choose models
```{r}
library (AICcmodavg); library (plyr); library (stringr)

models <- list (lm (propchange ~ log_mag, data = bind_reg_mag_ssps_st), 
                nls (propchange ~ I(log_mag^2*a)+ b*log_mag+c, data = bind_reg_mag_ssps_st, start = list (a=1, b=1, c=0)),
                nls (propchange ~ I((1/(log_mag+1)) * a)+ b, data = bind_reg_mag_ssps_st, start = list(a =1, b =1)),
                nls (propchange ~ I((1/(log_mag+1)) * a)+ b * log_mag, data = bind_reg_mag_ssps_st, start = list(a =1, b =1)),
                nls (propchange ~ a*I((log_mag+1)^b), data = bind_reg_mag_ssps_st, start = list (a=2, b=1.5)),
                lm  (propchange ~ poly(log_mag,3,raw=TRUE),data=bind_reg_mag_ssps_st),
                gam (propchange ~ s(log_mag), data = bind_reg_mag_ssps_st))

# models[[1]] # check for the regression coefficient
ldply (models, function(mod){ data.frame (AICc = AICc(mod), AIC = AIC(mod), model = deparse(formula(mod))) })

#1 deltaAICc: 12.4190 # 140.7691	140.6473	propchange ~ log_mag
#2 deltaAICc: 13.9356 # 142.2857	142.0816	propchange ~ I(log_mag^2 * a) + b * log_mag + c		
#3 deltaAICc: 15.0166 # 143.3667	143.2449	propchange ~ I((1/(log_mag + 1)) * a) + b		
#4 deltaAICc: 12.2890 # 140.6391	140.5173	propchange ~ I((1/(log_mag + 1)) * a) + b * log_mag
#5 deltaAICc: 11.9190 # 140.2691	140.1472	propchange ~ a * I((log_mag + 1)^b)
#6 deltaAICc: 15.8752 # 144.2253	143.9176	propchange ~ poly(log_mag, 3, raw = TRUE)
#7 deltaAICc:  0.0000 # 128.3501	127.1624	propchange ~ s(log_mag) ---------------------------the best


# #then, we choose three models:
# #linear:
# lm(propchange ~ log_mag,data=bind_reg_mag_ssps_st)%>%
#   summary()
# #non-linear1:
# nls (propchange ~ I((1/(log_mag+1)) * a)+ b * log_mag, data = bind_reg_mag_ssps_st, start = list(a =1, b =1))%>%
#   summary()
# #non-linear2:
# nls (propchange ~ a*I((log_mag+1)^b), data = bind_reg_mag_ssps_st, start = list (a=2, b=1.5))%>%
#   summary()



# # alternative choice is the Polynomial model
# lm(propchange~poly(log_mag,6,raw=TRUE),data=bind_reg_mag_ssps_st)%>%
#   summary()

#then, we choose the 3-degree model
# formula=y~poly(x,5,raw=TRUE)



#using gam to fit non-linear --------------------------- --------------------------- --------------------------- ---------------------------
#all data
gam(propchange ~ s(log_mag), data = bind_reg_mag_ssps_st)%>%
  summary()


#ssp1
sub_bind_reg_mag_ssp1_st <- subset(bind_reg_mag_ssps_st,group == "ssp1")
gam(propchange ~ s(log_mag), data = sub_bind_reg_mag_ssp1_st)%>%
  summary()
#ssp2
sub_bind_reg_mag_ssp2_st <- subset(bind_reg_mag_ssps_st,group == "ssp2")
gam(propchange ~ s(log_mag), data = sub_bind_reg_mag_ssp2_st)%>%
  summary()
#ssp5
sub_bind_reg_mag_ssp5_st <- subset(bind_reg_mag_ssps_st,group == "ssp5")
gam(propchange ~ s(log_mag), data = sub_bind_reg_mag_ssp5_st)%>%
  summary()
```

#Model performance
```{r}
# #Build the model
# model<-lm(propchange ~ log_mag,data=bind_reg_mag_ssps_st)
# #Make predictions
# predictions<-model%>%predict(bind_reg_mag_ssps_st)
# data.frame(
# RMSE=RMSE(predictions,bind_reg_mag_ssps_st$propchange),
# R2=R2(predictions,bind_reg_mag_ssps_st$propchange)
# )
# 
# #Build the model
# model<-nls (propchange ~ I((1/(log_mag+1)) * a)+ b * log_mag, data = bind_reg_mag_ssps_st, start = list(a =1, b =1))
# #Make predictions
# predictions<-model%>%predict(bind_reg_mag_ssps_st)
# data.frame(
# RMSE=RMSE(predictions,bind_reg_mag_ssps_st$propchange),
# R2=R2(predictions,bind_reg_mag_ssps_st$propchange)
# )
# 
# #Build the model
# model<-nls (propchange ~ a*I((log_mag+1)^b), data = bind_reg_mag_ssps_st, start = list (a=2, b=1.5))
# #Make predictions
# predictions<-model%>%predict(bind_reg_mag_ssps_st)
# data.frame(
# RMSE=RMSE(predictions,bind_reg_mag_ssps_st$propchange),
# R2=R2(predictions,bind_reg_mag_ssps_st$propchange)
# )


#Build the model --------------------------- --------------------------- --------------------------- --------------------------- --------------------------- 
model<-gam(propchange ~ s(log_mag), data = bind_reg_mag_ssps_st)
#Make predictions
predictions<-model%>%predict(bind_reg_mag_ssps_st)
data.frame(
RMSE=RMSE(predictions,bind_reg_mag_ssps_st$propchange),
R2=R2(predictions,bind_reg_mag_ssps_st$propchange)
)

```


#violin + scatter plotting
#_tot_
```{r}
sizetext <- 7

p1 <- ggplot(bind_mag_ssp1_st,aes(x=group,y=pred_cost_mean, fill = group))+
  geom_violin(width= 0.7)+
  # geom_jitter(position = position_jitter(seed = 1, width = 0.06), aes(colour = "#00000099"), size = 0.8, alpha = 0.5)+
  geom_jitter(width = 0.06, aes(colour = "#00000099"), size = 0.8, alpha = 0.65)+
  # geom_point(size=1,alpha=0.4,colour = "#00000099")+
  geom_line(aes(group=Country_name,color=direct),linewidth=0.2,alpha=0.8)+
  scale_color_manual(values = c("increase" = "#F2584B","decrease" = "#70AD47","no change" = "#4B4B4B")) +
  scale_fill_manual(values = c("#FD978070","#C5E0B470")) +
  scale_y_continuous(trans = 'log10', breaks = c(0,1,100,1000,10000,100000), labels = scales::comma)+
  theme_classic(base_size = sizetext)+
  theme(axis.ticks = element_line(colour = "black", linewidth = 0.2),
        axis.text = element_text(size = sizetext, colour = "black"),
        axis.title = element_text(size = sizetext), 
        axis.text.x = element_text(angle=30, hjust=1), legend.position = "none")+
  labs(x="", y="Potential economic cost\n(millions of US$)")

p2 <- ggplot(bind_mag_ssp2_st,aes(x=group,y=pred_cost_mean, fill = group))+
  geom_violin(width= 0.7)+
  # geom_jitter(position = position_jitter(seed = 1, width = 0.06), aes(colour = "#00000099"), size = 0.8, alpha = 0.5)+
  geom_jitter(width = 0.06, aes(colour = "#00000099"), size = 0.8, alpha = 0.65)+
  # geom_point(size=1,alpha=0.4,colour = "#00000099")+
  geom_line(aes(group=Country_name,color=direct),linewidth=0.2,alpha=0.8)+
  scale_color_manual(values = c("increase" = "#F2584B","decrease" = "#70AD47","no change" = "#4B4B4B")) +
  scale_fill_manual(values = c("#FD978070","#C5E0B470")) +
  scale_y_continuous(trans = 'log10', breaks = c(0,1,100,1000,10000,100000), labels = scales::comma)+
  theme_classic(base_size = sizetext)+
  theme(axis.ticks = element_line(colour = "black", linewidth = 0.2),
        axis.text = element_text(size = sizetext, colour = "black"),
        axis.title = element_text(size = sizetext), 
        axis.text.x = element_text(angle=30, hjust=1), legend.position = "none")+
  labs(x="", y="Potential economic cost\n(millions of US$)")

p3 <- ggplot(bind_mag_ssp5_st,aes(x=group,y=pred_cost_mean, fill = group))+
  geom_violin(width= 0.7)+
  # geom_jitter(position = position_jitter(seed = 1, width = 0.06), aes(colour = "#00000099"), size = 0.8, alpha = 0.5)+
  geom_jitter(width = 0.06, aes(colour = "#00000099"), size = 0.8, alpha = 0.65)+
  # geom_point(size=1,alpha=0.4,colour = "#00000099")+
  geom_line(aes(group=Country_name,color=direct),linewidth=0.2,alpha=0.8)+
  scale_color_manual(values = c("increase" = "#F2584B","decrease" = "#70AD47","no change" = "#4B4B4B")) +
  scale_fill_manual(values = c("#FD978070","#C5E0B470")) +
  scale_y_continuous(trans = 'log10', breaks = c(0,1,100,1000,10000,100000), labels = scales::comma)+
  theme_classic(base_size = sizetext)+
  theme(axis.ticks = element_line(colour = "black", linewidth = 0.2),
        axis.text = element_text(size = sizetext, colour = "black"),
        axis.title = element_text(size = sizetext), 
        axis.text.x = element_text(angle=30, hjust=1), legend.position = "none")+
  labs(x="", y="Potential economic cost\n(millions of US$)")


pdf(width = 4.2, height = 1.5, file = "fig6abc.pdf")
grid.arrange(p1, p2, p3, ncol=3)

dev.off()
```
#legend of violin + scatter
```{r}
pdf(width = 4.2, height = 1.5, file = "fig6abc-legend.pdf")
sizetext <- 7

ggplot(bind_mag_ssp1_st,aes(x=group,y=pred_cost_mean, fill = group))+
  geom_violin(width= 0.7)+
  # geom_jitter(position = position_jitter(seed = 1, width = 0.06), aes(colour = "#00000099"), size = 0.8, alpha = 0.5)+
  geom_jitter(width = 0.06, aes(colour = "#00000099"), size = 0.8, alpha = 0.65)+
  # geom_point(size=1,alpha=0.4,colour = "#00000099")+
  geom_line(aes(group=Country_name,color=direct),linewidth=0.2,alpha=0.8)+
  scale_color_manual(values = c("increase" = "#F2584B","decrease" = "#70AD47","no change" = "#4B4B4B")) +
  scale_fill_manual(values = c("#FD978070","#C5E0B470")) +
  scale_y_continuous(trans = 'log10', breaks = c(0,1,100,1000,10000,100000), labels = scales::comma)+
  theme_classic(base_size = sizetext)+
  theme(axis.ticks = element_line(colour = "black", linewidth = 0.2),
        axis.text = element_text(size = sizetext, colour = "black"),
        axis.title = element_text(size = sizetext), 
        axis.text.x = element_text(angle=30, hjust=1), legend.position = "bottom")+
  labs(x="", y="Potential economic cost\n(millions of US$)")
```




#each ssp group data fitting===============================================================
#non-linear regression plotting
#_tot_
```{r}
pdf(width = 12, height = 4, file = "fig6d_ssp1_2_5.pdf")

sizetext <- 12
sizepoint <- 3
sizename <- 2
my.formula1 <- y ~ s(x, k = 3)
my.formula2 <- y ~ x
my.formula3 <- y ~ I((1/(x + 1)) * a) + b * x
my.formula4 <- y ~ a * I((x + 1)^b)
my.formula5 <- y ~ poly(x,3,raw=TRUE)


ggplot(bind_reg_mag_ssps_st, aes(x = log_mag, y = propchange,color = factor(bind_reg_mag_ssps_st$group))) +
  geom_point(size = sizepoint, alpha = 0.65)+
  geom_text_repel(label = bind_reg_mag_ssps_st$show_Country_name, size = sizename,max.overlaps = 30, box.padding = 0.5,aes(color = factor(bind_reg_mag_ssps_st$group)))+
   scale_color_manual(values = c("ssp1"="#FED3C2","ssp2"="#FD9780","ssp5"="#611320"), 'Climate scenarios')+
  geom_hline(yintercept = 0, colour = "black", linewidth = 0.2, linetype = "dashed")+
   # scale_x_continuous(labels = scales::comma)+
   # scale_y_continuous(labels = scales::comma)+
  
  geom_smooth(method = "gam",
              formula = my.formula1,
              # color="#70AD47",
              linewidth=1, se=T, alpha = 0.3) +
  # geom_smooth(method = "lm",
  #             formula = my.formula3,
  #             color="#F78053",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula4,
  #             color="#3E7EBE",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula5,
  #             color="#FD9780",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula2,
  #             color="#4B4B4B",
  #             linewidth=1, se=T, alpha = 0.2) +
  
  theme_classic(base_size = sizetext)+
  theme(axis.ticks = element_line(colour = "black", linewidth = 0.2),
        axis.text = element_text(size = sizetext, colour = "black"),
        axis.title = element_text(size = sizetext), 
        axis.text.x = element_text(angle=30, hjust=1), legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        panel.background = element_rect(fill = 'white', colour = 'white'), 
        panel.grid.minor = element_line(color = 'white'), 
        panel.grid.major = element_line(color = 'white'))+
  labs(x="Potential proactive response capacity", y="Proportional change of\npotential total economic cost (%)")


dev.off()
```








#all data fitting===============================================================
#non-linear regression plotting
#_tot_
```{r}
pdf(width = 9.5, height = 4, file = "fig6d_all_new.pdf")

sizetext <- 12
sizepoint <- 3
sizename <- 2
my.formula1 <- y ~ s(x, k = 3)
my.formula2 <- y ~ x
my.formula3 <- y ~ I((1/(x + 1)) * a) + b * x
my.formula4 <- y ~ a * I((x + 1)^b)
my.formula5 <- y ~ poly(x,3,raw=TRUE)


ggplot(bind_reg_mag_ssps_st, aes(x = log_mag, y = propchange*100)) +
  geom_point(size = sizepoint, alpha = 0.65, aes(color = factor(bind_reg_mag_ssps_st$group)))+
  geom_text_repel(label = bind_reg_mag_ssps_st$show_Country_name, size = sizename,max.overlaps = 30, box.padding = 0.5,aes(color = factor(bind_reg_mag_ssps_st$group)))+
   scale_color_manual(values = c("ssp1"="#FED3C2","ssp2"="#FD9780","ssp5"="#611320"), 'Climate scenarios')+
  geom_hline(yintercept = 0, colour = "black", linewidth = 0.2, linetype = "dashed")+
   # scale_x_continuous(labels = scales::comma)+
   # scale_y_continuous(labels = scales::comma)+
  
  geom_smooth(method = "gam",
              formula = my.formula1,
              color="#70AD47",
              linewidth=1, se=T, alpha = 0.4) +
  # geom_smooth(method = "lm",
  #             formula = my.formula3,
  #             color="#F78053",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula4,
  #             color="#3E7EBE",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula5,
  #             color="#FD9780",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula2,
  #             color="#4B4B4B",
  #             linewidth=1, se=T, alpha = 0.2) +
  
  theme_classic(base_size = sizetext)+
  theme(axis.ticks = element_line(colour = "black", linewidth = 0.2),
        axis.text = element_text(size = sizetext, colour = "black"),
        axis.title = element_text(size = sizetext), 
        axis.text.x = element_text(angle=0, hjust=1), legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        panel.background = element_rect(fill = 'white', colour = 'white'), 
        panel.grid.minor = element_line(color = 'white'), 
        panel.grid.major = element_line(color = 'white'))+
  labs(x="Potential proactive response capacity", y="Proportional change of\npotential total economic cost (%)")


dev.off()
```






















#2024-10-14
#each trend data fitting===============================================================
#non-linear regression plotting
#_tot_



#choose models
```{r}
library (AICcmodavg); library (plyr); library (stringr)

bind_reg_mag_ssps_st_pos <- subset(bind_reg_mag_ssps_st, bind_reg_mag_ssps_st$trend == "positive")
bind_reg_mag_ssps_st_neg <- subset(bind_reg_mag_ssps_st, bind_reg_mag_ssps_st$trend == "negative")

models_pos <- list (lm (propchange ~ log_mag, data = bind_reg_mag_ssps_st_pos), 
                nls (propchange ~ I(log_mag^2*a)+ b*log_mag+c, data = bind_reg_mag_ssps_st_pos, start = list (a=1, b=1, c=0)),
                nls (propchange ~ I((1/(log_mag+1)) * a)+ b, data = bind_reg_mag_ssps_st_pos, start = list(a =1, b =1)),
                nls (propchange ~ I((1/(log_mag+1)) * a)+ b * log_mag, data = bind_reg_mag_ssps_st_pos, start = list(a =1, b =1)),
                nls (propchange ~ a*I((log_mag+1)^b), data = bind_reg_mag_ssps_st_pos, start = list (a=2, b=1.5)),
                lm  (propchange ~ poly(log_mag,3,raw=TRUE),data=bind_reg_mag_ssps_st_pos),
                gam (propchange ~ s(log_mag), data = bind_reg_mag_ssps_st_pos))

models_neg <- list (lm (propchange ~ log_mag, data = bind_reg_mag_ssps_st_neg), 
                # nls (propchange ~ I(log_mag^2*a)+ b*log_mag+c, data = bind_reg_mag_ssps_st_neg, start = list (a=1, b=1, c=0)),
                # nls (propchange ~ I((1/(log_mag+1)) * a)+ b, data = bind_reg_mag_ssps_st_neg, start = list(a =1, b =1)),
                # nls (propchange ~ I((1/(log_mag+1)) * a)+ b * log_mag, data = bind_reg_mag_ssps_st_neg, start = list(a =1, b =1)),
                # nls (propchange ~ a*I((log_mag+1)^b), data = bind_reg_mag_ssps_st_neg, start = list (a=2, b=1.5)),
                # lm  (propchange ~ poly(log_mag,3,raw=TRUE),data=bind_reg_mag_ssps_st_neg),
                gam (propchange ~ s(log_mag), data = bind_reg_mag_ssps_st_neg))

# models[[1]] # check for the regression coefficient
ldply (models_pos, function(mod){ data.frame (AICc = AICc(mod), AIC = AIC(mod), model = deparse(formula(mod))) })
ldply (models_neg, function(mod){ data.frame (AICc = AICc(mod), AIC = AIC(mod), model = deparse(formula(mod))) })



#1 deltaAICc: 12.4190 # 140.7691	140.6473	propchange ~ log_mag
#2 deltaAICc: 13.9356 # 142.2857	142.0816	propchange ~ I(log_mag^2 * a) + b * log_mag + c		
#3 deltaAICc: 15.0166 # 143.3667	143.2449	propchange ~ I((1/(log_mag + 1)) * a) + b		
#4 deltaAICc: 12.2890 # 140.6391	140.5173	propchange ~ I((1/(log_mag + 1)) * a) + b * log_mag
#5 deltaAICc: 11.9190 # 140.2691	140.1472	propchange ~ a * I((log_mag + 1)^b)
#6 deltaAICc: 15.8752 # 144.2253	143.9176	propchange ~ poly(log_mag, 3, raw = TRUE)
#7 deltaAICc:  0.0000 # 128.3501	127.1624	propchange ~ s(log_mag) ---------------------------the best


# #then, we choose three models:
# #linear:
# lm(propchange ~ log_mag,data=bind_reg_mag_ssps_st)%>%
#   summary()
# #non-linear1:
# nls (propchange ~ I((1/(log_mag+1)) * a)+ b * log_mag, data = bind_reg_mag_ssps_st, start = list(a =1, b =1))%>%
#   summary()
# #non-linear2:
# nls (propchange ~ a*I((log_mag+1)^b), data = bind_reg_mag_ssps_st, start = list (a=2, b=1.5))%>%
#   summary()



# # alternative choice is the Polynomial model
# lm(propchange~poly(log_mag,6,raw=TRUE),data=bind_reg_mag_ssps_st)%>%
#   summary()

#then, we choose the 3-degree model
# formula=y~poly(x,5,raw=TRUE)



#using gam to fit non-linear --------------------------- --------------------------- --------------------------- ---------------------------
#all data
gam(propchange ~ s(log_mag), data = bind_reg_mag_ssps_st)%>%
  summary()


#positive
sub_bind_reg_mag_ssp1_st <- subset(bind_reg_mag_ssps_st,trend == "positive")
gam(propchange ~ s(log_mag), data = sub_bind_reg_mag_ssp1_st)%>%
  summary()
#negative
sub_bind_reg_mag_ssp2_st <- subset(bind_reg_mag_ssps_st,trend == "negative")
gam(propchange ~ s(log_mag), data = sub_bind_reg_mag_ssp2_st)%>%
  summary()

```
#Model performance
```{r}
#positive
model<-gam(propchange ~ s(log_mag), data = sub_bind_reg_mag_ssp1_st)
#Make predictions
predictions<-model%>%predict(sub_bind_reg_mag_ssp1_st)
data.frame(
RMSE=RMSE(predictions,sub_bind_reg_mag_ssp1_st$propchange),
R2=R2(predictions,sub_bind_reg_mag_ssp1_st$propchange)
)

#negative
model<-gam(propchange ~ s(log_mag), data = sub_bind_reg_mag_ssp2_st)
#Make predictions
predictions<-model%>%predict(sub_bind_reg_mag_ssp2_st)
data.frame(
RMSE=RMSE(predictions,sub_bind_reg_mag_ssp2_st$propchange),
R2=R2(predictions,sub_bind_reg_mag_ssp2_st$propchange)
)
```

```{r}
pdf(width = 12, height = 4, file = "fig6d_positive_negat.pdf")

sizetext <- 12
sizepoint <- 3
sizename <- 2
my.formula1 <- y ~ s(x, k = 3)
my.formula2 <- y ~ x
my.formula3 <- y ~ I((1/(x + 1)) * a) + b * x
my.formula4 <- y ~ a * I((x + 1)^b)
my.formula5 <- y ~ poly(x,3,raw=TRUE)


ggplot(bind_reg_mag_ssps_st, aes(x = log_mag, y = propchange,fill = factor(bind_reg_mag_ssps_st$trend))) +
  geom_point(size = sizepoint, alpha = 0.65,aes(color = factor(bind_reg_mag_ssps_st$group)))+
  geom_text_repel(label = bind_reg_mag_ssps_st$show_Country_name, size = sizename,max.overlaps = 30, box.padding = 0.5,aes(color = factor(bind_reg_mag_ssps_st$group)))+
   scale_color_manual(values = c("ssp1"="#FED3C2","ssp2"="#FD9780","ssp5"="#611320"))+
   scale_fill_manual(values = c("positive"="#7772B2","negative"="#70AD47"))+
  geom_hline(yintercept = 0, colour = "black", linewidth = 0.2, linetype = "dashed")+
   # scale_x_continuous(labels = scales::comma)+
   # scale_y_continuous(labels = scales::comma)+
  
  geom_smooth(method = "gam",
              formula = my.formula1,
              # color="#70AD47",
              linewidth=1, se=T, alpha = 0.3) +
  # geom_smooth(method = "lm",
  #             formula = my.formula3,
  #             color="#F78053",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula4,
  #             color="#3E7EBE",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula5,
  #             color="#FD9780",
  #             linewidth=1, se=T, alpha = 0.2) +
  # geom_smooth(method = "lm",
  #             formula = my.formula2,
  #             color="#4B4B4B",
  #             linewidth=1, se=T, alpha = 0.2) +
  
  theme_classic(base_size = sizetext)+
  theme(axis.ticks = element_line(colour = "black", linewidth = 0.2),
        axis.text = element_text(size = sizetext, colour = "black"),
        axis.title = element_text(size = sizetext), 
        axis.text.x = element_text(angle=30, hjust=1), legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        panel.background = element_rect(fill = 'white', colour = 'white'), 
        panel.grid.minor = element_line(color = 'white'), 
        panel.grid.major = element_line(color = 'white'))+
  labs(x="Potential proactive response capacity", y="Proportional change of\npotential total economic cost (%)")


dev.off()
```








#2024-10-15
```{r}
bind_reg_mag_ssps_st_pos_neg_ssp1 <- subset(bind_reg_mag_ssps_st, bind_reg_mag_ssps_st$group == "ssp1")
bind_reg_mag_ssps_st_pos_neg_ssp1 %>%
  wilcox_test(Post_invasion_management ~ trend, paired = FALSE)

```
#plotting post-invasion management between negative and positive changes
```{r}
library(ggpubr)
pdf(width = 2, height = 4, file = "Extended Data Fig5.pdf")

sizetext <- 7
compare_list <- list(
    c("Negative","Positive"))

bind_reg_mag_ssps_st_pos_neg_ssp1$trend <- as.factor(bind_reg_mag_ssps_st_pos_neg_ssp1$trend)
ggplot(bind_reg_mag_ssps_st_pos_neg_ssp1,aes(x=trend,y=Post_invasion_management, fill = trend))+
  geom_violin(width= 0.7)+
  # geom_jitter(position = position_jitter(seed = 1, width = 0.06), aes(colour = "#00000099"), size = 0.8, alpha = 0.5)+
  geom_jitter(width = 0.06, aes(colour = "#00000099"), size = 0.8, alpha = 0.65)+
  # geom_point(size=1,alpha=0.4,colour = "#00000099")+
  # geom_line(aes(group=Country_name,color=direct),linewidth=0.2,alpha=0.8)+
  # scale_color_manual(values = c("increase" = "#F2584B","decrease" = "#70AD47","no change" = "#4B4B4B")) +
  scale_fill_manual(values = c("Positive" = "#FD978070","Negative" = "#C5E0B470")) +
  # scale_y_continuous(trans = 'log10', breaks = c(0,1,100,1000,10000,100000), labels = scales::comma)+
  theme_classic(base_size = sizetext)+
  theme(axis.ticks = element_line(colour = "black", linewidth = 0.2),
        axis.text = element_text(size = sizetext, colour = "black"),
        axis.title = element_text(size = sizetext), 
        axis.text.x = element_text(angle=30, hjust=1), legend.position = "none")+
  labs(x="", y="Count of post-invasion management")+
  stat_compare_means(
    comparisons = compare_list,
    method = "wilcox.test",paired = F,
    label = "p.signif")

dev.off()
```

